---
title: "Modeling Run"
author: "Nathan Basch"
date: "Last compiled on `r  paste0(format(Sys.time(), tz='America/New_York'), ' EST')`"
params:
  run_name: "local"
  blurb: "Local development"
  path: "utils/model_report/Example"
  PR_link: "None"
  Jira_link: "None"
  save_results: FALSE
  model_to_save: "main_rf"
  split_pct: 0.9
  group_split_var: !expr NULL
  strata_var: !expr NULL
  n_folds: 5
  recipes_to_run: !expr c("main", "mainwidth")
  models_to_run: !expr c("xgb", "rf")
  models_to_explain: !expr c("main_rf")
  explain_data: "Train"
  error_colours: !expr NULL
  run_stack: TRUE
  run_explainer: TRUE
  run_cache: FALSE
  run_visualization: TRUE
output:
  rmdformats::material:
    code_folding: hide
    thumbnails: FALSE
    lightbox: TRUE
    highlight: tango
  pdf_document: default
description: "This is the model output for a supply shed baseline modeling run"
always_allow_html: true
---

```{r setup, include=FALSE}
options(dplyr.summarise.inform = FALSE)



library(rstudioapi)
library(here)
library(reactable)
library(dplyr)
# if (params$run_name == "local"){
# setwd(dirname(getActiveDocumentContext()$path))       # Set working directory to source file location
# }

# knitr::opts_knit$set(root.dir = dirname(getActiveDocumentContext()$path))
knitr::opts_knit$set(root.dir = file.path(here::here()))
knitr::opts_chunk$set(cache.path = file.path(here::here(),params$path, "cache/"))

input_path<-file.path(params$path, "src")

```

# Welcome!

This document is a template workflow to show the machine learning development process. Included are the following tabs:

-   **Data and features:** A description of data, cleaning methodology and features

-   **Tidymodels setup:** A setup of model engines and feature engineering "recipes"

-   **Tuning and Metrics:** Executions summaries of model performance

-   **Explain**: Metrics to "explain" aspects of black box models

-   **Map:** A map to investigate if there is any geographic patterns of error

These are the parameters used in this specific run:

```{r param_tbl, message=FALSE}

t<-params
class(t) <- "list"
sapply(t[!sapply(t, purrr::is_empty)], paste, collapse = ', ')%>%
  as.data.frame()%>%
  rename("value(s)" = 1)%>%
  reactable()

```


```{r child = "children/data_child.Rmd"}
```


```{r child = "children/tidymodels_setup_child.Rmd"}
```


```{r child = "children/tuning_metrics_child.Rmd"}
```


```{r child = "children/explain_child.Rmd"}
```



# Summary


```{r summary_table, message=FALSE}
# Trying to put this on top of report:
# https://stackoverflow.com/questions/23570718/creating-summaries-at-the-top-of-a-knitr-report-that-use-variables-that-are-defi
# {r chunk-a, ref.label=c('tune_rf','param_table')}

  # rmses%>%
  # filter(rank == min(rank))%>%
  # rename("best_model" = m)%>%
  # FormatReactable(filt = F)
  
  

```
