---
title: "data_child"
output: html_document
---


# Data and features {.tabset}



## Load data
```{r packages, include=FALSE}
# Call file to load data
source(file.path(here(),input_path,"packages.R"),local = knitr::knit_global())

```


```{r load_data, message=FALSE, cache = params$run_cache, fig.width=10, fig.height = 5,out.width="100%"}
# Call file to load data
source(file.path(here(),input_path,"load_data.R"),echo = TRUE, local = knitr::knit_global())


```

## Clean Data

See data cleaning code below.

```{r clean_data, message=FALSE, fig.width=10, fig.height = 5,out.width="100%"}

# Call file to clean data
source(file.path(here(),input_path,"clean_data.R"),echo = TRUE, local = knitr::knit_global(), max.deparse.length=1e3)

vis_miss(df,warn_large_data = F)

```

Below is the entire dataset (with all original columns), which you can feel free to filter and explore.

```{r df_reactable, message=FALSE, warning=FALSE}
# Show top 50 rows
FormatReactable(head(df))
```

## Features

See https://custom-scripts.sentinel-hub.com/custom-scripts/sentinel/sentinel-2/ for definition of some of the different remote sensing indices. 

```{r show_features, include=F}
source(file.path(here(),input_path,"features_outcome.R"),echo = TRUE, local = knitr::knit_global())


```

Our Outcome variable is **`r outcome_var`** .

Our potential predictor variables are **`r predict_vars`** .

## EDA

Below is some exploratory data analysis showing i) a histogram of all numeric columns, and ii) the frequencies of all categorical columns in the data

```{r eda_all_columns, message=FALSE, warning=FALSE, fig.show="hold", fig.width=10,out.width="50%", dpi=300}

PlotNumericColumns(df%>%dplyr::select(predict_vars, outcome_var))
PlotCategoricalColumns(df%>%dplyr::select(predict_vars))


# Boxplot (x = year, y = total emisisons) Facet by crop

# cor_df<-cor(df%>%dplyr::select(where(is.numeric))%>%as_tibble())
# corrplot(cor_df)

```

Below is a correlation plot of all numeric variables
```{r correlation_plot, message=FALSE, warning=FALSE, fig.show="hold", fig.width=10,dpi=300}

cor_df<-cor(df%>%dplyr::select(predict_vars,outcome_var)%>%dplyr::select(where(is.numeric))%>%as_tibble())
corrplot(cor_df, method = 'color', order = 'alphabet', tl.cex = 0.5)

```


Below is the relationship between each variable and the outcome variable
```{r plot_vs_outcome, message=FALSE, warning=FALSE, fig.show="hold", fig.width=10,out.width="50%", dpi=300}

PlotNumericColumnsVOutcome(df%>%dplyr::select(predict_vars,outcome_var), outcome_var)
PlotCategoricalColumnsVOutcome(df%>%dplyr::select(predict_vars,outcome_var), outcome_var)


```

Below is all missing data.

```{r eda_missing, message=FALSE, warning=FALSE, fig.width=10, fig.height = 5,out.width="100%"}
# Missing data
vis_miss(df%>%dplyr::select(predict_vars, outcome_var))

```