---
title: "Untitled"
output: html_document
---

# Tidymodels setup {.tabset}

To run these models, we will use the tidymodels framework. Each tab below represents a key step in developing a model. These steps will all come together to become a [Workflowset](https://workflowsets.tidymodels.org/) that we are able to tune

To read more, see [tidymodels.org](https://www.tidymodels.org/start/).

## Split data

Below is the code for how we split data into training and test. Note that we are also setting up **`r params$n_folds`**-fold cross validation.

```{r training_test}
# browser()
# Split data into training and test set --------------------
source("scripts/training_test.R", echo = TRUE, local = knitr::knit_global())

```

```{r training_test_folds, eval=params$n_folds > 1}

# Split training set into k-fold cross validation for evaluation later
source("scripts/folds.R",echo = TRUE, local = knitr::knit_global())

```

Below are some visualizations that show how the test and training data differ

```{r show_splits, warning=FALSE,message=FALSE, fig.show="hold", fig.width=10,out.width="50%", eval=params$run_visualization}

#Visualize training and test data
PlotNumericColumns(df_train%>%mutate(dataset = "train")%>%bind_rows(df_test%>%mutate(dataset = "test"))%>%
                     dplyr::select(predict_vars, outcome_var, dataset),
                   fill_column = "dataset")
PlotCategoricalColumns(df_train%>%mutate(dataset = "train")%>%bind_rows(df_test%>%mutate(dataset = "test"))%>%
                   dplyr::select(predict_vars, dataset),
                   fill_column = "dataset")


# df %>% ggplot(aes(x = area_ac, y = total_co2eq_kg_ac, colour = region)) +geom_point()
```


```{r plot_vs_outcome_splits, message=FALSE, warning=FALSE, fig.show="hold", fig.width=10,out.width="50%", dpi=300, eval=params$run_visualization}

PlotNumericColumnsVOutcome(df_train%>%mutate(dataset = "train")%>%bind_rows(df_test%>%mutate(dataset = "test"))%>%
                     dplyr::select(predict_vars, outcome_var, dataset),
                     outcome = outcome_var,
                   colour_column = "dataset")
PlotCategoricalColumnsVOutcome(df_train%>%mutate(dataset = "train")%>%bind_rows(df_test%>%mutate(dataset = "test"))%>%
                   dplyr::select(predict_vars, dataset, outcome_var),
                   outcome = outcome_var,
                   fill_column = "dataset")

```


```{r show_splits_fips, warning=FALSE,message=FALSE,fig.width=10,out.width="100%"}

# Insert some custom EDA here.

# By fips code
# PlotCategoricalColumns(df_train%>%mutate(dataset = "train")%>%bind_rows(df_test%>%mutate(dataset = "test"))%>%
#                      dplyr::select(loc_fips, dataset),
#                    fill_column = "dataset")+
#   theme(axis.text=element_text(size=5))





```

## Specs

Below are the specs (models) we are considering in our workflow.

```{r specs, warning=FALSE}
source(file.path(here(),input_path,"specs.R"),echo = TRUE,local = knitr::knit_global())


```

## Recipes

We may be considering different sets of predictors and/or different feature engineering steps. We define those below.

```{r recipes, warning=FALSE}
source(file.path(here(),input_path,"recipes.R"),echo = TRUE,local = knitr::knit_global())

```

## Workflowset

Recipes and Specs combine to create a workflowset, which is just an object that contains each model we will be training.

```{r workflow_set, warning=FALSE}

# Create workflowset
source("scripts/create_workflowset.R",echo = TRUE, local = knitr::knit_global())

```

In total there are **`r nrow(df_wf_set)`** total models, which we summarize below:

```{r workflow_set_reactable, warning=FALSE, message=FALSE}
df_wf_set%>%
  rowwise()%>%
  mutate(
        predictors = paste(info$workflow[[1]]$pre$actions$recipe$recipe$var_info%>%filter(role == "predictor")%>%pull(variable), collapse = "<br>"),
         outcome =  paste(info$workflow[[1]]$pre$actions$recipe$recipe$var_info%>%filter(role == "outcome")%>%pull(variable),   collapse = ","),
        outcome_predictors = paste("<b>Outcome</b>",
                           outcome,
                           "<br><b>Predictors</b>",
                           predictors,
                           sep = "<br>"),
        operations = paste(capture.output(info$workflow[[1]]$pre$actions$recipe$recipe)[-(1:10)], collapse = "<br><br>"),
         workflow_output = paste(capture.output(info$workflow, type = "output"), collapse = "<br>"))%>%
  dplyr::select(wflow_id, outcome_predictors:workflow_output)%>%
    reactable(
            columns = list(workflow_output = colDef(html = TRUE, width = 1000),
                           operations = colDef(html = TRUE),
                           outcome_predictors = colDef(html = TRUE, width = 250)

                           ),
            outlined = TRUE,
              highlight = TRUE,
              striped = TRUE,
              showSortable = TRUE,
              compact = FALSE,
              bordered = TRUE,
              defaultExpanded = F,
              filterable = TRUE,
              showPageSizeOptions = TRUE)

```